Dynamical Stochastic Approximation Monte Carlo

### 2018-02-22 papers/histogram/sad.tex
data update with sad paper figure change.

~\jpsays{Add N50 ff0.1 and N50 ff0.3 and remove sticky-wall!}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/lv/ww1_30-ff0_22-30x4-max-entropy-error.pdf}
  \caption{The average entropy error for each method is shown with
  SAD serving as the `golden'
  standard.}\label{fig:avgS-30x4}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/lv/ww1_30-ff0_22-60x8-max-entropy-error.pdf}
  \caption{The average entropy error for each method is shown with SAD serving as
  the `golden' standard.}\label{fig:avgS-60x8}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/lv/ww1_30-ff0_22-100x10-max-entropy-error}
  \caption{The average entropy error for each method is shown with
    WL-TMMC using a cutoff of 10$^{-10}$ serving as the
    standard.}\label{fig:avgS-100x10}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_20-N50-max-entropy-error.pdf}
  \caption{The average entropy error is shown with TMI acting as the
  `golden' standard.}\label{fig:N50-mean-error}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N500-max-entropy-error.pdf}
  \caption{The average entropy error is shown with TMI acting as the
  `golden' standard.}
\end{figure}

>>>>

~\jpsays{Add N50 ff0.1 and N50 ff0.3 and remove sticky-wall!}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N50-max-entropy-error.pdf}
  \caption{The average entropy error for each method is shown with
  SAD serving as the `golden'
  standard.}\label{fig:avgS-30x4}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_10-N50-max-entropy-error.pdf}
  \caption{The average entropy error for each method is shown with SAD serving as
  the `golden' standard.}\label{fig:avgS-60x8}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/lv/ww1_30-ff0_22-100x10-max-entropy-error}
  \caption{The average entropy error for each method is shown with
    WL-TMMC using a cutoff of 10$^{-10}$ serving as the
    standard.}\label{fig:avgS-100x10}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_20-N50-max-entropy-error.pdf}
  \caption{The average entropy error is shown with TMI acting as the
  `golden' standard.}\label{fig:N50-mean-error}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N500-max-entropy-error.pdf}
  \caption{The average entropy error is shown with TMI acting as the
  `golden' standard.}
\end{figure}
